Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-09-26 ejap.manuscript.RMD
added abbreviation table

@@

# Statements and Declarations
????

# Abbreviations
Make a table for this

@@

# AUTHOR CONTRIBUTIONS
Conceived and designed research: Stian Ellefsen, Håvard Hamarsland, Daniel Hammarström.
Performed experiments: Kristian Lian, Daniel Hammarström, Håvard Hamarsland, Håvard Nygaard, Sara Christine Moen.
Interpreted results of experiments: Kristian Lian, Daniel Hammarström.
Prepared Figures: Kristian Lian, Daniel Hammarström.
Drafted manuscripts: Kristian Lian, Daniel Hammarström.
Edited and revised manuscript: Stian Ellefsen, Håvard Hamarsland, Daniel Hammarström.
Approved final version of the manuscript: .

@@

  ## Make it to flextable
  flextable() %>%
  ## Change headers
  compose(i = 1, j = c(1, 2, 3, 4, 5, 6, 7, 8, 9), part = "header", 
          value = c(as_paragraph("Sex"),
                    as_paragraph("n"), 
                    as_paragraph("Age (yrs)"), 
                    as_paragraph("Stature (cm)"), 
                    as_paragraph("Body mass (kg)"),
                    as_paragraph("Lean mass (kg)"),
                    as_paragraph("60\U00BA sec", as_sup("-1")), 
                    as_paragraph("240\U00BA sec", as_sup("-1")), 
                    as_paragraph("0\U00BA sec", as_sup("-1")))) %>%
  add_header_row(values = c(" ", "Knee-extension peak torque"), colwidths = c(6, 3)) %>%
  set_caption("Table 1. Participant characteristics")

dxa.flex <- border(dxa.flex, 
                     i = NULL,
                     j = NULL,
                     border = NULL,
                     border.top = fp_border_default(color = "grey"),
                     border.bottom = fp_border_default(color = "grey"),
                     border.left = fp_border_default(color = "grey"),
                     border.right = fp_border_default(color = "grey"),
                     part = "all")

@@

## Flextable
primer.tab <- tab.dat %>%
  flextable() %>%
  compose(i = 1, j = c(1, 2, 3, 4), part = "header",
          value = c(as_paragraph("Gene"),
                    as_paragraph("Sequence (forward - reverse)"),
                    as_paragraph("Ct mean (SD)"),
                    as_paragraph("E"))) %>%
  set_caption("Table 2. Primer Sequences") %>%
  set_table_properties(layout = "autofit")

primer.tab <- border(primer.tab, 
                     i = NULL,
                     j = NULL,
                     border = NULL,
                     border.top = fp_border_default(color = "grey"),
                     border.bottom = fp_border_default(color = "grey"),
                     border.left = fp_border_default(color = "grey"),
                     border.right = fp_border_default(color = "grey"),
                     part = "all")

>>>>

```{r abbreviation table}
### Abbreviations table

## Data
abbreviations.dat <- read_excel("./data/abbreviations.xlsx")

tab.dat <- abbreviations.dat

## Flextable
abb.tab <- tab.dat %>%
  flextable() %>%
  set_caption(caption = "Abbreviations",
              align_with_table = FALSE) %>%
  set_table_properties(layout = "autofit")

abb.tab <- delete_part(x = abb.tab, part = "header")

abb.tab <- border(abb.tab, 
                     i = NULL,
                     j = NULL,
                     border = NULL,
                     border.top = fp_border_default(color = "black"),
                     border.bottom = fp_border_default(color = "black"),
                     border.left = fp_border_default(color = "black"),
                     border.right = fp_border_default(color = "black"),
                     part = "all")

abb.tab
```

@@

# Statements and Declarations
This study was financed through research funds from the Inland Norway University of Applied Sciences. There were no economical vested interest and everyone participating as researchers and associates, received only a regular salary during this study.

@@

# AUTHOR CONTRIBUTIONS
Conceived and designed research: SE, HH, DH.
Performed experiments: KL, DH, HH, HN, SCM.
Interpreted results of experiments: KL, DH.
Prepared Figures: KL, DH.
Drafted manuscripts: KL, DH.
Edited and revised manuscript: SE, HH, DH.
Approved final version of the manuscript: .

@@

  ## Make it to flextable
  flextable() %>%
  ## Change headers
  compose(i = 1, j = c(1, 2, 3, 4, 5, 6, 7, 8, 9), part = "header", 
          value = c(as_paragraph("Sex"),
                    as_paragraph("n"), 
                    as_paragraph("Age (yrs)"), 
                    as_paragraph("Stature (cm)"), 
                    as_paragraph("Body mass (kg)"),
                    as_paragraph("Lean mass (kg)"),
                    as_paragraph("60\U00BA sec", as_sup("-1")), 
                    as_paragraph("240\U00BA sec", as_sup("-1")), 
                    as_paragraph("0\U00BA sec", as_sup("-1")))) %>%
  add_header_row(values = c(" ", "Knee-extension peak torque"), colwidths = c(6, 3)) %>%
  set_caption(caption = "Table 1. Participant characteristics",
              align_with_table = FALSE)

dxa.flex <- border(dxa.flex, 
                     i = NULL,
                     j = NULL,
                     border = NULL,
                     border.top = fp_border_default(color = "black"),
                     border.bottom = fp_border_default(color = "black"),
                     border.left = fp_border_default(color = "black"),
                     border.right = fp_border_default(color = "black"),
                     part = "all")

@@

## Flextable
primer.tab <- tab.dat %>%
  flextable() %>%
  compose(i = 1, j = c(1, 2, 3, 4), part = "header",
          value = c(as_paragraph("Gene"),
                    as_paragraph("Sequence (forward - reverse)"),
                    as_paragraph("Ct mean (SD)"),
                    as_paragraph("E"))) %>%
  set_caption(caption = "Table 2. Primer Sequences",
              align_with_table = FALSE) %>%
  set_table_properties(layout = "autofit")

primer.tab <- border(primer.tab, 
                     i = NULL,
                     j = NULL,
                     border = NULL,
                     border.top = fp_border_default(color = "black"),
                     border.bottom = fp_border_default(color = "black"),
                     border.left = fp_border_default(color = "black"),
                     border.right = fp_border_default(color = "black"),
                     part = "all")
